working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2018-12-19 Manuscript_draft/Manuscript_draft.Rmd
edits

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species. The y axis is the proportion of ovules converted to seed in percentage. The different, treatments which are presented in the legend are, hand cross pollination, hand self pollination, natural selfing and apomixis. More information about this treatments can be found in Methods and Appendices."}

@@

ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_bw()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species. The y axis is the proportion of ovules converted to seed in percentage. The different treatments (N=10) which are presented in the legend are, hand cross pollination, hand self pollination, natural selfing and apomixis. More information about these treatments can be found in Methods and Appendices."}

@@

ggplot(bio,aes(x=Species,y=value,fill=variable))+
  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"), legend.text=element_text(size=7))+
  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

### 2018-12-19 Manuscript_draft/Manuscript_draft.tex
edits

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{Barplot with the different treatments that provide information
of the reproductive biology of the ten species. The y axis is the
proportion of ovules converted to seed in percentage. The different,
treatments which are presented in the legend are, hand cross
pollination, hand self pollination, natural selfing and apomixis. More
information about this treatments can be found in Methods and
Appendices.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{Barplot with the different treatments that provide information
of the reproductive biology of the ten species. The y axis is the
proportion of ovules converted to seed in percentage. The different
treatments (N=10) which are presented in the legend are, hand cross
pollination, hand self pollination, natural selfing and apomixis. More
information about these treatments can be found in Methods and
Appendices.}
\end{figure}
